SoK: The Evolution of Defenses Against Web Application Attacks

### 2014-11-12 docs/questioning.tex
more stylistic changes

\begin{enumerate}
\item We provide an exploitation model that puts application attacks
  based on source code injection under a common
  perspective.
\item We categorize and analyze proposed defenses using a set of
  criteria that are important for building protection mechanisms.
\item We find that researchers often test the accuracy
  of their mechanisms poorly. 
\item We also find that researchers do not often make their mechanisms
  available to the community, thus no one can either use their
  mechanism, or replicate their experiments.
\item We discuss how our observations may be the main reasons why the
  mechanisms are not adopted in practice.
\item We discuss what are the necessary criteria for new mechanisms
  and how our work can help researchers to design new countermeasures.
\end{enumerate}

@@

@@

{\it Diglossia}~\cite{SMS13} combines positive taint tracking (see
Subsubsection~\ref{sec:taint}) together with parse-tree validation.
Diglossia was based on the theory of Ray and Ligatti~\cite{RL12b}
(also see Section~\ref{sec:attacks}) to detect {\sc dsl} code
injection attacks. In addition, it is actually the first, and so far
the only framework that detects No{\sc sql} injection attacks. When an
application computes an output string (query), Diglossia computes a
``shadow" of this string. Specifically, it maps all characters
introduced by the application to a shadow character set. This set does
not contain any characters coming from the tainted input. Then, the
scheme creates the tree of the query that is about to be executed and
compares it with the parsed tree of the ``shadow" (Point {\sc e}i{\sc q}). If
the trees are not equal the application is probably under attack. Note
that Diglossia can be bypassed in the same way as other taint
tracking approaches as described in reference~\cite{NBR14}.
%% PL which way is this exactly?

\begin{landscape}
\begin{table}
\scalebox{0.99}{
	& \bf{Attack} \\
  &   {\it {\sc sqlg}uard}~\cite{BWS05} & 243 & ({\sc na},{\sc na},{\sc na},{\sc na})\_{\bf ?} & 3\% ({\sc s}) & {\sc sql} injection \\
  &   {\it {\sc sqlc}heck}~\cite{SW06} & 402 & (36848,7648,0,0)\_r & 3ms per query ({\sc s}) & {\sc sql} injection \\
  &   {\it CsFire}~\cite{DDHPJ10} & 35 & (419582,1141807,0,3)\_r\tnote{4} & {\sc na} ({\sc c}) & {\sc csrf} \\
  &   {\it {\sc sql}rand}~\cite{BK04} & 286 & (3,{\sc na},{\sc na},0)\_a & $\le$6.5{\it ms} ({\sc s}) & {\sc sql} injection \\
  &   {\it {\sc sm}ask}~\cite{JB07} & 27 & (5,{\sc nq},{\sc nq},{\sc nq})\_r  & {\sc na} ({\sc s}) & {\sc sql} injection, {\sc xss} \\
  &   {\it Haldar et al.}~\cite{HCF05} & 177 & (2,{\sc na},{\sc na},0)\_s & {\sc nq} ({\sc s}) & {\sc sql} injection, {\sc xss} \\ 
	&  	{\sc csse}~\cite{PB05} & 312 & (7,{\sc nq},{\sc nq},{\sc nq})\_r & 2--10\% ({\sc s}) & {\sc sql} injection, {\sc xp}ath, {\sc xss} \\
	&  	{\it Xu et al.}~\cite{XBS06} & 297 & (9,{\sc nq},0,{\sc nq})\_r & average 76\% ({\sc s}) & {\sc sql} injection, {\sc xss} \\ 
  &  	{\it {\sc wasc}}~\cite{NLC07} & 31 & ({\sc nq},{\sc nq},{\sc nq},{\sc nq})\_r & up to 30\% ({\sc s}) & {\sc sql} injection, {\sc xss} \\
	&  	{\it {\sc php} Aspis}~\cite{PMP11} & 12 & (12,{\sc nq},{\sc nq},2)\_r & 2.2$\times$ ({\sc s}) & {\sc sql} and {\sc php} injection, {\sc xss} \\
  &   {\it {\sc didafit}}~\cite{LLW02} & 85 & ({\sc na},{\sc na},{\sc na},{\sc na})\_{\bf ?} & {\sc na} ({\sc s}) & {\sc sql} injection \\
	&   {\it {\sc amnesia}}~\cite{HO05,HO06,HO05b} & 118,66,376 & (1470,{\sc nq},0,0)\_a & {\sc nq} ({\sc s}) & {\sc sql} injection \\ 
	&   {\it libAnomaly}~\cite{VMV05} & 226 & (9,15987,60,0)\_r & 0.20--1{\it ms} per query ({\sc s}) & {\sc sql} injection \\
	& 	{\it {\sc sd}river}~\cite{MS09,MKS09,MKLS11} & 21,8,5 & (241,{\sc nq},0,0)\_a & 39\% ({\sc s}) & {\sc sql} and {\sc xp}ath injection \\
  &   {\it Diglossia}~\cite{SMS13} & 4 & (9,{\sc nq},{\sc nq},{\sc nq})\_r & 13\% ({\sc s}) & {\sc sql} and No{\sc sql} injection \\
	{\sc nq} (Not Quantified) indicates that a requirement is mentioned in the publication
          fp}) and False Negatives ({\sc fn}). For every quadruple there is a corresponding suffix that indicates whether the testbed was
	based on: a) real-world applications known to be vulnerable ({\it r}), b) synthetic benchmarks ({\it s}), c) both ({\it a}).
    \item[4] The numbers of this quadruple involve requests.
\end{table}
\end{landscape}

@@

\scalebox{0.99}{

>>>>

\begin{enumerate}
\item We provide an exploitation model that puts application attacks
  based on source code injection under a common
  perspective.
\item We categorize and analyze proposed defenses using a set of
  criteria that are important for building protection mechanisms.
\item We find that researchers often test the accuracy
  of their mechanisms poorly. 
\item We also find that researchers do not often make their mechanisms
  available to the community, thus no one can either use them,
  or replicate their experiments.
\item We discuss how our observations may be the main reasons why the
  mechanisms are not adopted in practice.
\item We discuss what are the necessary criteria for new mechanisms
  and how our work can help researchers to design new countermeasures.
\end{enumerate}

@@

\scalebox{0.93}{
  & \bf{Attack}\tnote{4} \\
  &   {\it {\sc sqlg}uard}~\cite{BWS05} & 243 & ({\sc na},{\sc na},{\sc na},{\sc na})\_{\bf ?} & 3\% ({\sc s}) & {\sc sql}i \\
  &   {\it {\sc sqlc}heck}~\cite{SW06} & 402 & (36848,7648,0,0)\_r & 3ms per query ({\sc s}) & {\sc sql}i \\
  &   {\it CsFire}~\cite{DDHPJ10} & 35 & (419582,1141807,0,3)\_r\tnote{5} & {\sc na} ({\sc c}) & {\sc csrf} \\
  &   {\it {\sc sql}rand}~\cite{BK04} & 286 & (3,{\sc na},{\sc na},0)\_a & $\le$6.5{\it ms} ({\sc s}) & {\sc sql}i \\
  &   {\it {\sc sm}ask}~\cite{JB07} & 27 & (5,{\sc nq},{\sc nq},{\sc nq})\_r  & {\sc na} ({\sc s}) & {\sc sql}i, {\sc xss} \\
  &   {\it Haldar et al.}~\cite{HCF05} & 177 & (2,{\sc na},{\sc na},0)\_s & {\sc nq} ({\sc s}) & {\sc sql}i, {\sc xss} \\ 
  &   {\sc csse}~\cite{PB05} & 312 & (7,{\sc nq},{\sc nq},{\sc nq})\_r & 2--10\% ({\sc s}) & {\sc sql}i, {\sc xp}athi, {\sc xss} \\
  &   {\it Xu et al.}~\cite{XBS06} & 297 & (9,{\sc nq},0,{\sc nq})\_r & average 76\% ({\sc s}) & {\sc sql}i, {\sc xss} \\ 
  &   {\it {\sc wasc}}~\cite{NLC07} & 31 & ({\sc nq},{\sc nq},{\sc nq},{\sc nq})\_r & up to 30\% ({\sc s}) & {\sc sql}i, {\sc xss} \\
  &   {\it {\sc php} Aspis}~\cite{PMP11} & 12 & (12,{\sc nq},{\sc nq},2)\_r & 2.2$\times$ ({\sc s}) & {\sc sql}i and {\sc php}i, {\sc xss} \\
  &   {\it {\sc didafit}}~\cite{LLW02} & 85 & ({\sc na},{\sc na},{\sc na},{\sc na})\_{\bf ?} & {\sc na} ({\sc s}) & {\sc sql}i \\
  &   {\it {\sc amnesia}}~\cite{HO05,HO06,HO05b} & 118,66,376 & (1470,{\sc nq},0,0)\_a & {\sc nq} ({\sc s}) & {\sc sql}i \\ 
  &   {\it libAnomaly}~\cite{VMV05} & 226 & (9,15987,60,0)\_r & 0.20--1{\it ms} per query ({\sc s}) & {\sc sql}i \\
  &   {\it {\sc sd}river}~\cite{MS09,MKS09,MKLS11} & 21,8,5 & (241,{\sc nq},0,0)\_a & 39\% ({\sc s}) & {\sc sql}i and {\sc xp}athi \\
  &   {\it Diglossia}~\cite{SMS13} & 4 & (9,{\sc nq},{\sc nq},{\sc nq})\_r & 13\% ({\sc s}) & {\sc sql}i and No{\sc sql}i \\
  {\sc nq} (Not Quantified) indicates that a requirement is mentioned in the\newline publication
          fp}) and False Negatives ({\sc fn}). For every quadruple\newline there is a corresponding suffix that indicates whether the testbed was
  based on: a) real-world applications known to be vulnerable ({\it r}), b) synthetic\newline benchmarks ({\it s}), c) both ({\it a}).
    \item[4] {\it i} stands for injection.
    \item[5] The numbers of this quadruple involve requests.

@@

{\it Diglossia}~\cite{SMS13} combines positive taint tracking (see
Subsubsection~\ref{sec:taint}) together with parse-tree validation.
Diglossia was based on the theory of Ray and Ligatti~\cite{RL12b}
(also see Section~\ref{sec:attacks}) to detect {\sc dsl} code
injection attacks. In addition, it is actually the first, and so far
the only framework that detects No{\sc sql} injection attacks. When an
application computes an output string (query), Diglossia computes a
``shadow" of this string. Specifically, it maps all characters
introduced by the application to a shadow character set. This set does
not contain any characters coming from the tainted input. Then, the
scheme creates the tree of the query that is about to be executed and
compares it with the parsed tree of the ``shadow" (Point {\sc e}i{\sc q}). If
the trees are not equal the application is probably under attack. Note
that Diglossia can be bypassed in the same way as other taint
tracking approaches as described in reference~\cite{NBR14}.

@@

\scalebox{0.93}{
